---
title: "GeoLift Incrementality Report"
subtitle: "`r params$experiment_name`"
date: "`r params$generated_at`"
output:
  pdf_document:
    toc: false
    latex_engine: xelatex
    fig_width: 7
    fig_height: 4
geometry: margin=1in
fontsize: 11pt
params:
  experiment_name:  "Experiment"
  kpi:              "Revenue"
  test_type:        "single"
  geo_level:        "DMA"
  channel:          "Meta"
  test_start:       ""
  test_end:         ""
  spend:            0
  lift_pct:         0
  lift_ci_low:      0
  lift_ci_high:     0
  att_total:        0
  p_value:          0.05
  iroas:            0
  pre_period_r2:    0
  pre_period_mape:  0
  n_cells:          1
  generated_at:     ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
library(knitr)
```

---

## Experiment Summary

| Field | Value |
|:------|:------|
| **Experiment** | `r params$experiment_name` |
| **KPI** | `r params$kpi` |
| **Test Type** | `r tools::toTitleCase(params$test_type)`-Cell |
| **Geo Level** | `r params$geo_level` |
| **Channel** | `r params$channel` |
| **Test Window** | `r params$test_start` → `r params$test_end` |
| **Total Spend** | $`r format(params$spend, big.mark=",")` |

---

## Key Results

```{r results-table}
results_df <- data.frame(
  Metric = c(
    "Incremental KPI (Total)",
    "Lift %",
    "90% Confidence Interval",
    "p-value",
    "iROAS",
    "Pre-period Fit (R²)",
    "Pre-period MAPE"
  ),
  Value = c(
    formatC(params$att_total, format="f", digits=0, big.mark=","),
    paste0("+", round(params$lift_pct, 2), "%"),
    paste0("[", round(params$lift_ci_low, 2), "%, ", round(params$lift_ci_high, 2), "%]"),
    round(params$p_value, 4),
    if (!is.null(params$iroas) && !is.na(params$iroas))
      paste0(round(params$iroas, 2), "×") else "—",
    round(params$pre_period_r2, 4),
    paste0(round(params$pre_period_mape, 2), "%")
  )
)
knitr::kable(results_df, col.names=c("Metric","Value"), align=c("l","r"))
```

---

## Statistical Validity

```{r validity}
checks <- data.frame(
  Check = c("Pre-period fit (R²)", "MAPE", "p-value", "CI lower bound"),
  Status = c(
    ifelse(params$pre_period_r2 >= 0.95, "✓ Pass", "⚠ Review"),
    ifelse(params$pre_period_mape <= 3,   "✓ Pass", "⚠ Review"),
    ifelse(params$p_value <= 0.05,         "✓ Significant", "— Not significant"),
    ifelse(params$lift_ci_low > 0,         "✓ Positive lower bound", "— Includes zero")
  )
)
knitr::kable(checks, col.names=c("Check","Result"), align=c("l","l"))
```

---

## Interpretation

```{r interpretation, results='asis'}
sig   <- params$p_value <= 0.05
valid <- params$pre_period_r2 >= 0.95 && params$pre_period_mape <= 3
pos   <- params$lift_pct > 0

if (sig && valid && pos) {
  cat(paste0(
    "**Result: Statistically significant positive lift detected.**\n\n",
    params$channel, " advertising generated a **+", round(params$lift_pct, 1),
    "% lift** in ", params$kpi, " (p = ", round(params$p_value, 3), "). ",
    "The result is supported by a strong pre-period synthetic control fit (R² = ",
    round(params$pre_period_r2, 3), "), confirming model validity.\n\n",
    if (!is.null(params$iroas) && !is.na(params$iroas) && params$iroas > 0)
      paste0("At an iROAS of **", round(params$iroas, 2), "×**, the campaign ",
             ifelse(params$iroas >= 3.3, "exceeds", "falls below"),
             " the 3.3× break-even threshold.") else ""
  ))
} else {
  cat(paste0(
    "**Result: No statistically significant lift detected.**\n\n",
    "The experiment did not produce a significant result at the 95% confidence level ",
    "(p = ", round(params$p_value, 3), "). ",
    if (!valid) "Pre-period model fit was insufficient — results should be interpreted with caution. " else "",
    "Consider extending the test duration or adjusting market selection before re-running."
  ))
}
```

---

*Report generated by GeoLift · `r params$generated_at`*
